The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-12-15 paper/mri_paper.tex
amplitude func 1 hmri

We conduct a full study of the MRI parameter space, focussed on the behavior with changing magnetic Prandtl number ($\mathrm{Pm} \equiv \frac{\mathrm{Rm}}{\mathrm{Re}} \equiv \frac{\nu}{\eta}$). In protoplanetary disks, as well as in liquid metal MRI experiments, the magnetic Prandtl number can be very small ($\mathrm{Pm} \sim 10^{-6}$). The scale separations caused by these large ratios of diffusivity to viscosity render the small Prandtl number regime inaccessible to simulations. This analytic formulation allows us to explore the behavior down to magnetic Prandtl numbers of $10^{-6}$ or lower.

@@

>>>>

We conduct a full study of the MRI parameter space, focussed on the behavior with changing magnetic Prandtl number ($\mathrm{Pm} \equiv \frac{\mathrm{Rm}}{\mathrm{Re}} \equiv \frac{\nu}{\eta}$). In protoplanetary disks, as well as in liquid metal MRI experiments, the magnetic Prandtl number can be very small ($\mathrm{Pm} \sim 10^{-6}$). The scale separations caused by these large ratios of diffusivity to viscosity render the small Prandtl number regime inaccessible to simulations. Because we solve spectrally in only one dimension, rather than in two or three, our analytic formulation allows us to explore the behavior down to magnetic Prandtl numbers of $10^{-6}$ or lower.

@@

In the above,

\beq
\mathcal{H} = \left[\begin{matrix}
0 & 0 & 0 & \partial_x \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\ \end{matrix} \right].
\eeq

The first amplitude equation (\ref{ampeq1}) therefore becomes

\begin{multline}
\label{ampeq1_hmri}
a \partial_T \alpha \, = - \, c \alpha \left|\alpha^2\right| \, - \, \widetilde{c} \alpha \partial_Z \beta \,  - b i k_c \alpha \, + \, h \partial_Z^2 \alpha \, \\
+ \, g i k_c^3 \alpha \, + \, q \xi \partial_Z^2 \alpha \, + \, w i k_c \xi \alpha,
\end{multline}

\beq
q = \left< \mathbb{V}^\dagger \cdot \left(\mathcal{H} \mathbb{V}_{21}\right)^* \right>,
\eeq

\beq
w = \left< \mathbb{V}^\dagger \cdot \left(\mathcal{H} \mathbb{V}_{11}\right)^*\right>.
\eeq
